Trajectory model of passive kelp dispersal

### 2020-07-23 thesis_chapter_3.Rmd
updated references and added in raft-longevity

and so,
$$m = (V_{stipesail}+V_{stipekeel})p_{ice} =(1 + \frac{p_w}{p_w -p{ice}})V_{stipesail}p_{ice}$$
To calculate the volume of the stipe a idealised cyliderical form is used with height being subsituted for height such that:
$$V = \pi r^2 l$$

>>>>

and so,
$$m = (V_{stipesail}+V_{stipekeel})p_{ice} =(1 + \frac{p_w}{p_w -p{ice}})V_{stipesail}p_{ice}$$
To calculate the volume of the stipe a idealised cyliderical form is used with height being subsituted for height such that:
$$V = \pi r^2 l$$
# Raft-longevity

Raft-longevity refers to the time a macroalgae raft remians afloat at the surface of the ocean after detachment. Raft-longevity was estimated from past studies by @graiff2016 and @graiff2013; which found mean raft times of approximately 30 days in moderate conditions.
